Class Paper - Introduction to Bayesian Statistics

### 2019-04-28 Paper_Output.Rmd

##Conclusions

Dolor sapiente consequatur aut error dolorem ut eum. Qui quod molestiae ut. Delectus libero quis ut placeat. Similique delectus dolores vitae nemo. Dolores officiis cum et reprehenderit perferendis iusto.

@@

>>>>

##Next Steps

Three steps are be necessary in order to strengthen the inference strategy, and draw clear conclusions from the results. First, issues with model estimation, related the problematic $\beta{age}$ and  $\beta{age^{2}}$ terms, should be resolved. It is possible that the literature has guidance on handling quadratics; and also possible quadratics simply do not work well with Bayesian models. Specifying priors for these variables differently; or else adopting an entirely functional form (such as a series of categorical dummies).

Second, additional model specifications should be explored. The control for district-level AfD vote seems necessary [^12], but complicates interpretation and should be considered more carefully. Initial exploration, using pre-election data, shows that the omission of constituency vote share does not greatly affect findings for other variables; however, this has not been thoroughly explored. Constituency was chosen as a convenient level of analysis, but neighbourhood or municipal-level characteristics might actually have a larger effect on political attitudes. People's views are likely to be shaped by the places where they spend their daily lives. More generally, controls were chosen arbitrarily, and might not be ideal. Measures of occupational class, religiosity, and housing status might be relevant; at an aggregate level, the distinction between East and West German states might also be relevant. A good strategy for estimating quadratic terms would aid in the exploration of additional specificaitons, because it could greatly speed model estimation and therefore make robustness checks practical.[^13]

Finally, the broader issues around selection bias and causal inference must be addressed. This is a separate question, outside Bayesian estimation. It is one that the literature has rarely answered in a satisfactory manner. The use of large-scale panel data is one possible solution. Showing how peoples' political views change *after* they move to more diverse neighbourhoods or workplaces would provide stronger evidence. This requires access to relatively rare data sources, but may not be impossible. Good research design should start with "what is ideal" and *then* move to "what is achievable."

There are three purely methodological challenges that this paper did not explore in great depth - but that a longer version woudl ideally explore. First, the paper uses both univariate and multivariate priors, but does not systematically compare their results. Benchmarking these two approaches (both their "accuracy" and their computational speed) would be interesting. This paper also implements basic missing-data handling -- but does not implement complicated imputation models, or compare fully Bayesian imputation with conventional (semi-Bayesian?) multiple imputation. This would be a useful extension. Finally, the paper currently does not consider any model selection or hypothesis testing techniques. Given the relatively simple hypotheses considered, these are probably not strictly necessary -- but they would nonetheless be a useful exercise. There are many topics to explore, both substantively and methodologically, following this initial work.

@@

[^12]: It is logically necessary that people in an AfD-supporting constituency are more likely to be AfD supports. Constituenecy-level variables that are correlated with AfD vote share would therefore *appear* correlated with individual-level AfD support, even if the correlation is spurious.

[^13]: Informal experimentation with various sets of variables is often a part of model-building. Computationally intensive models impose discipline, by contraining experimentation. This can be helpful, because it avoids overfitting and demands good theory. However, it might require a stronger theory than I had when pursuing this project.
